### 2015-05-23 docs/report/context.tex

>>>>

The reason why there are two kinds of context is because there will usually be data that does not need to be passed to the Web Workers with each chain, so having a global context allows this. Additionally, the local context allows users to avoid polluting the global one with keys that are not necessary for all operations.

We created a benchmark to explore the difference between sending the context and chains to execute as part of the same message, and using two different messages. The code for the benchmark is in the following listing:
\bmcode{http://jsperf.com/additional-sendingdata-comparison/2}{../../spikes/6.1/sendingAdditionalsSeqVsPar/jspBenchmark.js}

The results for the benchmark are displayed in Figure~\ref{fig:context-send}.
\img{Comparing small context message passing}{../../spikes/6.1/sendingAdditionalsSeqVsPar/jspBenchmark-all-browsers}{fig:context-send}
